---
title: "03_04_results_julia"
author: "Brendan Barrett"
date: "4/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rethinking)
library(RColorBrewer)
library(stringi)
source("02_01_plot_fcns.R")



```
## Individual Learning
Lets look at individual learning, not much to write home about here. 
We cannot estimate a ton of variation in \phi as they are almost always successful.
```{r il}
load("/Users/bbarrett/Documents/bias_i_sa_30/ind.rds")
fit_i <- stanfit
post_ind <- extract(fit_i)

precis(fit_i , pars=c("log_lambda","logit_phi") , depth=3)

DensLambda(post_ind)

DensLambda(post_ind , individual=TRUE , age_sex = FALSE)

z <- precis(fit_i , pars="log_lambda" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

DensPhi(post_ind)

DensPhi(post_ind , individual=TRUE , age_sex = FALSE)

z <- precis(fit_i , pars="logit_phi" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

plot(precis(fit_i , pars="sigma_i" , depth=3))

plot(precis(fit_i , pars="Rho_i" , depth=3))
```

## Frequency Dependent Social Learning
```{r fdsll}
load("/Users/bbarrett/Documents/bias_i_sa_30/freq.rds")
fit_freq <- stanfit
post_freq <- extract(fit_freq)

precis(fit_freq , pars=c("log_lambda","logit_phi","logit_gamma" , "log_f") , depth=3)

#lambda
DensLambda(post_freq)

DensLambda(post_freq , individual=TRUE , age_sex = FALSE)

z <- precis(fit_freq , pars="log_lambda" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#phi
DensPhi(post_freq)

DensPhi(post_freq , individual=TRUE , age_sex = FALSE)

z <- precis(fit_freq , pars="logit_phi" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#gamma
DensGamma(post_freq)

DensGamma(post_freq , individual=TRUE , age_sex = FALSE)

z <- precis(fit_freq , pars="logit_gamma" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#fc
DensFc(post_freq)

DensFc(post_freq , individual=TRUE , age_sex = FALSE)

z <- precis(fit_freq , pars="log_f" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#vcov stuff
plot(precis(fit_freq , pars="sigma_i" , depth=3))

plot(precis(fit_freq , pars="Rho_i" , depth=3))
```
## Male Biased Linear Social Learning

```{r mblsl}
load("/Users/bbarrett/Documents/bias_i_sa_30/male_lin.rds")
fit_male_lin <- stanfit
post_male_lin <- extract(fit_male_lin)

precis(fit_male_lin  , pars=c("log_lambda","logit_phi","logit_gamma") , depth=3)

#lambda
DensLambda(post_male_lin )

DensLambda(post_male_lin  , individual=TRUE , age_sex = FALSE)

z <- precis(fit_male_lin  , pars="log_lambda" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#phi
DensPhi(post_male_lin )

DensPhi(post_male_lin  , individual=TRUE , age_sex = FALSE)

z <- precis(fit_male_lin  , pars="logit_phi" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#gamma
DensGamma(post_male_lin )

DensGamma(post_male_lin  , individual=TRUE , age_sex = FALSE)

z <- precis(fit_male_lin  , pars="logit_gamma" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#vcov stuff
plot(precis(fit_male_lin  , pars="sigma_i" , depth=3))

plot(precis(fit_male_lin  , pars="Rho_i" , depth=3))
```

## Adult-biased Linear social learning

```{r ablsl}
load("/Users/bbarrett/Documents/bias_i_sa_30/adult_lin.rds")
fit_adult_lin <- stanfit
post_adult_lin <- extract(fit_adult_lin)

precis(fit_adult_lin  , pars=c("log_lambda","logit_phi","logit_gamma") , depth=3)

#lambda
DensLambda(post_adult_lin )

DensLambda(post_adult_lin  , individual=TRUE , age_sex = FALSE)

z <- precis(fit_adult_lin  , pars="log_lambda" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#phi
DensPhi(post_adult_lin )

DensPhi(post_adult_lin  , individual=TRUE , age_sex = FALSE)

z <- precis(fit_adult_lin  , pars="logit_phi" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#gamma
DensGamma(post_adult_lin )

DensGamma(post_adult_lin  , individual=TRUE , age_sex = FALSE)

z <- precis(fit_adult_lin  , pars="logit_gamma" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#vcov stuff
plot(precis(fit_adult_lin  , pars="sigma_i" , depth=3))

plot(precis(fit_adult_lin  , pars="Rho_i" , depth=3))
```

## Roost-biased social learning
```{r roostb sl}
load("/Users/bbarrett/Documents/bias_i_sa_30/roost_cue.rds")
fit_roost<- stanfit
post_roost <- extract(fit_roost)


precis(fit_roost , pars=c("log_lambda","logit_phi","logit_gamma" , "betaq") , depth=3)

#lambda
DensLambda(post_roost)

DensLambda(post_roost , individual=TRUE , age_sex = FALSE)

z <- precis(fit_roost , pars="log_lambda" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#phi
DensPhi(post_roost)

DensPhi(post_roost , individual=TRUE , age_sex = FALSE)

z <- precis(fit_roost , pars="logit_phi" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#gamma
DensGamma(post_roost)

DensGamma(post_roost , individual=TRUE , age_sex = FALSE)

z <- precis(fit_roost , pars="logit_gamma" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#fc
DensBetaq(post_roost)

DensBetaq(post_roost , individual=TRUE , age_sex = FALSE)

z <- precis(fit_roost , pars="betaq" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#vcov stuff
plot(precis(fit_roost , pars="sigma_i" , depth=3))

plot(precis(fit_roost , pars="Rho_i" , depth=3))
```

## Male-biased social learning
```{r  male b sl}
load("/Users/bbarrett/Documents/bias_i_sa_30/male_cue.rds")
fit_male <- stanfit
post_male <- extract(fit_male)

precis(fit_male , pars=c("log_lambda","logit_phi","logit_gamma" , "betaq") , depth=3)

#lambda
DensLambda(post_male)

DensLambda(post_male , individual=TRUE , age_sex = FALSE)

z <- precis(fit_male , pars="log_lambda" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#phi
DensPhi(post_male)

DensPhi(post_male , individual=TRUE , age_sex = FALSE)

z <- precis(fit_male , pars="logit_phi" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#gamma
DensGamma(post_male)

DensGamma(post_male , individual=TRUE , age_sex = FALSE)

z <- precis(fit_male , pars="logit_gamma" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#fc
DensBetaq(post_male)

DensBetaq(post_male , individual=TRUE , age_sex = FALSE)

z <- precis(fit_male , pars="betaq" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#vcov stuff
plot(precis(fit_male , pars="sigma_i" , depth=3))

plot(precis(fit_male , pars="Rho_i" , depth=3))
```

#Adult-biased social learning

```{r  adult b sl}
load("/Users/bbarrett/Documents/bias_i_sa_30/adult_cue.rds")
fit_adult <- stanfit
post_adult <- extract(fit_adult)

precis(fit_adult , pars=c("log_lambda","logit_phi","logit_gamma" , "betaq") , depth=3)

#lambda
DensLambda(post_adult)

DensLambda(post_adult , individual=TRUE , age_sex = FALSE)

z <- precis(fit_adult , pars="log_lambda" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#phi
DensPhi(post_adult)

DensPhi(post_adult , individual=TRUE , age_sex = FALSE)

z <- precis(fit_adult , pars="logit_phi" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#gamma
DensGamma(post_adult)

DensGamma(post_adult , individual=TRUE , age_sex = FALSE)

z <- precis(fit_adult , pars="logit_gamma" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#fc
DensBetaq(post_adult)

DensBetaq(post_adult , individual=TRUE , age_sex = FALSE)

z <- precis(fit_adult , pars="betaq" , depth=3)
z@row.names <- PlotRenameAgeSex(z@row.names)
plot(z)

#vcov stuff
plot(precis(fit_adult , pars="sigma_i" , depth=3))

plot(precis(fit_adult , pars="Rho_i" , depth=3))
```

## Information Criteria
First we can make table of Information Criteria. These should not be treated as truth, but can be informative of general performance. We should evaluate model prediction and compare parameter predictions across models.
```{r waictab}
waic_tab <- compare(fit_i , fit_freq, fit_male , fit_adult , fit_roost , fit_male_lin , fit_adult_lin)
waic_tab
```