---
title: "03_results summary"
author: "Julia Penndorf & Brendan Barrett & Lucy Aplin"
date: "9/23/2021"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(rethinking)
library(rstan)
library(janitor)
library(beepr)
library(DescTools)#ramp legend
library(RColorBrewer)
```

# Overview
We fit 6 EWA models to start with. In this instance it was from the 60s window only foir the BA group. 
Social learning could occur on the first timestep, and $A_{t,k}=0$.
Now lets load files of model fits. I will run these longer on the final iteration.
```{r load rds and script , echo=FALSE}
source("02_01_plot_fcns.R")
fit_i <- readRDS("/Users/bbarrett/Downloads/fit_i_60s_slu_all.rds")
fit_freq <- readRDS("/Users/bbarrett/Downloads/fit_freq_60s_slu_all.rds")
fit_adult <- readRDS("/Users/bbarrett/Downloads/fit_adult_60s_slu_all.rds")
fit_male <-  readRDS("/Users/bbarrett/Downloads/fit_male_60s_slu_all.rds")
fit_rank <-  readRDS("/Users/bbarrett/Downloads/fit_rank_60s_slu_all.rds")
fit_roost <-  readRDS("/Users/bbarrett/Downloads/fit_roost_60s_slu_all.rds")
fit_rank_freq <-  readRDS("/Users/bbarrett/Downloads/fit_rank_freq_60s_slu_all.rds")
fit_adult_freq <-  readRDS("/Users/bbarrett/Downloads/fit_adult_freq_60s_slu_all.rds")
fit_male_freq <-  readRDS("/Users/bbarrett/Downloads/fit_male_freq_60s_slu_all.rds")

d <- read.csv("cockatoo_data/ALL_ROOSTS_Almonds_cockatoo_60s.csv")
d$subject_index <- as.integer(as.factor(d$subject) )
d <- clean_names(d)

str(d)
d <- d[with(d, order(subject_index,date, rel_time)), ]

d$bout <- rep(0,nrow(d))
ff <- rep(0,length(unique(d$subject)))
for (r in 1:nrow(d)) {
  for(i in 1:length(unique(d$subject_index))) {
    if( d[r,"subject_index"]==i){ #this is temporary due to zeros
      ff[i] <-ff[i] + 1
      d$bout[r] <- ff[i]
    }
  }
}
beep(2)
d$tech_index <- as.integer(as.factor(d$behav1))
```
## Information Criteria
First we can look at WAIC scores, although these should not be treated religiously.
They can give us an overall understanding of variation in the models in predicting the data while penalizing overfitting.But there are caveats with information criteria and time series models.
```{r info criteria , eval=FALSE}
ic_tab <- compare(fit_i , fit_freq, fit_male , fit_adult , fit_roost , fit_rank , fit_adult_freq , fit_rank_freq , fit_male_freq)
ic_tab
```
Overall we see the most support for the frequency dependent model with with a weight of `r `ic_tab$weight[1]$` and WAIC=`r `ic_tab$WAIC[1]$`.
We see comparable support for roost, rank and male models, with less support for adult. No strong evidence for pure social learning.

The combo models did not get great support, so I am ignoring them in the meantime. We could plot model predictions but there seems to be plenty to do.
# Frequency Dependent Learning
```{r fdep , eval=TRUE}
precis(fit_freq , pars=c('lambda' , 'phi' , 'fc' , 'sigma_i') , depth=2)
precis(fit_i , pars=c('Rho_i') , depth=3)
plot(precis(fit_freq , pars=c( 'fc_i' ) , depth=2)
)
post_freq <- extract(fit_freq)
DensLambda(post_freq)
DensPhi(post_freq)
DensGamma(post_freq)
DensFc(post_freq)
```


This is the best supported model. We see that `r sum(post_freq$fc>1)/length(post_freq$fc)` of the posterior mass is greater than 1, which is consistent with conformist transmission, and the maximum a posteriori (MAP) estimate is $f_c=$`r chainmode( post_freq$fc , adj=0.01 )`.

We will also make heatmap plots for each individual based off of the frequency dependent learning model.
```{r}
d$median_choose_red_freq <- apply(post_freq$PrPreds[,,2] , 2 ,  median)
d$median_choose_red_ind <- apply(post_ind$PrPreds[,,2] , 2 , median)
d$median_choose_red_freq <- apply(post_freq$PrPreds[,,2] , 2 ,  median)
d$median_choose_red_male <- apply(post_male$PrPreds[,,2] , 2 ,  median)
d$median_choose_red_adult <- apply(post_adult$PrPreds[,,2] , 2 ,  median)
d$median_choose_red_roost <- apply(post_roost$PrPreds[,,2] , 2 ,  median)
d$median_choose_red_rank <- apply(post_rank$PrPreds[,,2] , 2 ,  median)

colMain <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(101))# reverse pallette of ramped colors from 0 to 1 by 0.1 so red in 1 and blue is 0

###BA
dd <- d[d$group=="BA",]
dd$subject_group_index <- as.integer(as.factor(dd$subject_index))
plot(dd$subject_group_index ~ dd$time_hh_min , cex=0.5 , pch=19 ,
     col=colMain[round(dd$median_choose_red_freq*100)] , main="Group BA"   ) 
ColorLegend(x=max(dd$time_hh_min) + 50 ,y=max(dd$subject_group_index), 
            cols=colMain , labels=seq(from=0 , to=1 , by=0.1) , cex=0.8)


plot(dd$rank_index ~ dd$time_hh_min , cex=0.5 , pch=19 ,
     col=colMain[round(dd$median_choose_red_freq*100)] , main="Group BA"   ) 

### CG
dd <- d[d$group=="CG",]
dd$subject_group_index <- as.integer(as.factor(dd$subject_index))
plot(dd$subject_group_index ~ dd$rel_time , cex=0.5 , pch=19 ,
     col=colMain[round(dd$median_choose_red_freq*100)] , main="Group CG"   ) 
ColorLegend(x=max(dd$rel_time) + 50 ,y=max(dd$subject_group_index), 
            cols=colMain , labels=seq(from=0 , to=1 , by=0.1) , cex=0.8)

plot(dd$rank_index ~ dd$rel_time , cex=0.5 , pch=19 ,
     col=colMain[round(dd$median_choose_red_freq*100)] , main="Group CG"   ) 

#NB
dd <- d[d$group=="NB",]
dd$subject_group_index <- as.integer(as.factor(dd$subject_index))
plot(dd$rank_index ~ dd$rel_time , cex=0.5 , pch=19 ,
     col=colMain[round(dd$median_choose_red_freq*100)] , main="Group NB"   ) 
ColorLegend(x=max(dd$rel_time) + 50 ,y=max(dd$subject_group_index), 
            cols=colMain , labels=seq(from=0 , to=1 , by=0.1) , cex=0.8)

```

# Roost-biased Learning
```{r}
post_roost <- extract(fit_roost)
precis(fit_roost , pars=c('lambda' , 'phi' , 'gamma' , 'betaq'))
# precis(fit_roost , pars='lambda_i' , depth=2)
# precis(fit_roost , pars='phi_i' , depth=2)
# precis(fit_roost , pars='gamma_i' , depth=2)
# precis(fit_roost , pars='betaq_i' , depth=2)

DensLambda(post_roost)
DensPhi(post_roost)
DensGamma(post_roost)
DensBetaq(post_roost)
```

# Male-biased learning
```{r}
post_male <- extract(fit_male)
#str(post_male)

precis(fit_male , pars=c('lambda' , 'phi' , 'gamma' , 'betaq'))
# precis(fit_male , pars='lambda_i' , depth=2)
# precis(fit_male , pars='phi_i' , depth=2)
# precis(fit_male , pars='gamma_i' , depth=2)
# precis(fit_male , pars='betaq_i' , depth=2)

DensLambda(post_male)
DensPhi(post_male)
DensGamma(post_male)
DensBetaq(post_male)

```
# Rank-biased learning
```{r}
post_rank <- extract(fit_rank)

precis(fit_rank , pars=c('lambda' , 'phi' , 'gamma' , 'betaq'))
# precis(fit_rank , pars='lambda_i' , depth=2)
# precis(fit_rank , pars='phi_i' , depth=2)
# precis(fit_rank , pars='gamma_i' , depth=2)
# plot(precis(fit_rank , pars='betaq_i' , depth=2))

DensLambda(post_rank)
DensPhi(post_rank)
DensGamma(post_rank)
DensBetaq(post_rank)
```
# Adult-biased learning
```{r}
post_adult <- extract(fit_adult)

precis(fit_adult , pars=c('lambda' , 'phi' , 'gamma' , 'betaq'))
# precis(fit_adult , pars='lambda_i' , depth=2)
# precis(fit_adult , pars='phi_i' , depth=2)
# precis(fit_adult , pars='gamma_i' , depth=2)
# precis(fit_adult , pars='betaq_i' , depth=2)

DensLambda(post_adult)
DensPhi(post_adult)
DensGamma(post_adult)
DensBetaq(post_adult)
```
# Individual Learning
```{r il , eval=TRUE}
precis(fit_i , pars=c('lambda' , 'phi' , 'sigma_i') , depth=2)
precis(fit_i , pars=c('Rho_i') , depth=3)
post_ind <- extract(fit_i)
DensLambda(post_ind)
DensPhi(post_ind)
```

```{r}
#plots conditions
colz <- c( "blue" , "red")
pchez <- c(1,19)
col_strat <- brewer.pal( 6 ,"YlOrRd" )

par(mfrow = c(4, 2))
par(cex = 0.7)
par(mar = c(4, 4, 2, .1), oma = c(.1, .1 , .1, .1))
for(i in 1:max(d$subject_index)){
  data <- d[d$subject_index==i,]
  plot(rep(1.03 , nrow(data)) ~ data$bout , ylim=c(0,1.04) , ylab="Post Med Prob Choose Red" , xlab="foraging bout" ,
       col=colz[data$tech_index] , pch=pchez[data$open + 1] , cex=.5 )
  abline(h=1)
  lines(data$median_choose_red_ind ~ data$bout , col=col_strat[1])
  lines(data$median_choose_red_freq ~ data$bout , col=col_strat[2] )
  lines(data$median_choose_red_male ~ data$bout , col=col_strat[3] )
  lines(data$median_choose_red_adult ~ data$bout , col=col_strat[4] )
  lines(data$median_choose_red_roost ~ data$bout , col=col_strat[5] )
  lines(data$median_choose_red_rank ~ data$bout , col=col_strat[6] )
  
  title(main = paste0("ID=",unique(data$subject),", Group=",unique(data$group),", Sex=",unique(data$sex_index),", Age=",unique(data$age_index)) , cex.main=1)
  legend("bottomleft" , fill=col_strat , legend=c("IL" , "FDSL" , "MaleBSL" , "AdultBSL" , "RoostBSL" , "RankBSL") , bty='n' , cex=0.5 )
}

#all individuals
```